Symbiont shuffling linked to differential photochemical efficiency of *Symbiodinium* in three Caribbean reef corals

### 2017-11-01 analysis/analysis.Rmd
Figure adjustments for publication

## Plot Figure 1
```{r Fig1}
png("figures/Fig1.png", width=4, height=2.5, units="in", res=300)
par(mfrow=c(1, 3), mar=c(3,3,1.1,0), mgp=c(1.5, 0.1, 0), 
    tcl=0.2, cex.axis=0.8, xaxs="i")
plot(NA, xlim=c(0, 1), ylim=c(0.2, 0.55),
     xlab="Proportion D1a", ylab=expression(italic(F[v]/F[m])))
mtext("A.", adj=-0.2, font=2)
with(subset(pred, Species=="Of" & time=="init"), {
  lines(fit ~ PropD, lty=1, lwd=1)
  addpoly(PropD, lci, uci, col=alpha("#1b9e77", 0.5))
})
with(subset(pred, Species=="Of" & time=="bleach"), {
  lines(fit ~ PropD, lty=2, lwd=2)
  addpoly(PropD, lci, uci, col=alpha("#1b9e77", 0.5))
})

par(mar=c(3,1.5,1.1,1.5))
plot(NA, xlim=c(0, 1), ylim=c(0.2, 0.55),
     xlab="Proportion D1a", ylab="")
mtext("B.", adj=-0.2, font=2)
with(subset(pred, Species=="Ss" & time=="init"), {
  lines(fit ~ PropD, lty=1, lwd=1)
  addpoly(PropD, lci, uci, col=alpha("#7570b3", 0.5))
})
with(subset(pred, Species=="Ss" & time=="bleach"), {
  lines(fit ~ PropD, lty=2, lwd=2)
  addpoly(PropD, lci, uci, col=alpha("#7570b3", 0.5))
})

par(mar=c(3,0,1.1,3))
plot(NA, xlim=c(0, 1), ylim=c(0.2, 0.55),
     xlab="Proportion D1a", ylab="")
mtext("C.", adj=-0.2, font=2)
with(subset(pred, Species=="Mc" & time=="init"), {
  lines(fit ~ PropD, lty=1, lwd=1)
  addpoly(PropD, lci, uci, col=alpha("#d95f02", 0.5))
})
with(subset(pred, Species=="Mc" & time=="bleach"), {
  lines(fit ~ PropD, lty=2, lwd=2)
  addpoly(PropD, lci, uci, col=alpha("#d95f02", 0.5))
})
dev.off()
```
![Figure 1. Photochemical efficiency as a function of the proportion of clade D *Symbiodinium*. Solid lines represent ambient conditions, and dotted lines represent the relationship under heat stress (32°C). Shaded regions represent 90% confidence intervals around fitted values.](../figures/Fig1.png)

@@

```{r Fig3}
# Figure 3
png("figures/Fig3.png", width=7, height=3.5, units="in", res=300)
par(mfrow=c(1, 2), mar=c(3,3,1,1), mgp=c(1.5, 0.1, 0), tcl=0.2, cex.axis=0.8)
## Figure 3A: Final vs. initial proportion clade D
plot(NA, xlim=c(0,1), ylim=c(0,1), xaxs="i", yaxs="i",
     xlab="Prop. D1a before bleaching",
     ylab="Prop. D1a after recovery")
# Plot lines for low bleaching
with(subset(res.Low, Species=="Mc"), {
  lines(fit ~ PropD.init, lwd=2, col="#d95f02", xpd=NA)
  addpoly(PropD.init, lower, upper, col = alpha("#d95f02", 0.4))
  Mc.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.Low, Species=="Of"), {
  lines(fit ~ PropD.init, lwd=2, col="#1b9e77", xpd=NA)
  addpoly(PropD.init, lower, upper, col = alpha("#1b9e77", 0.4))
  Of.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.Low, Species=="Ss"), {
  lines(fit ~ PropD.init, lwd=2, col="#7570b3", xpd=NA)
  addpoly(PropD.init, lower, upper, col = alpha("#7570b3", 0.4))
  Ss.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
abline(0,1, lty=1, lwd=0.5)
# Plot lines for Med bleaching
with(subset(res.Med, Species=="Mc"), {
  lines(fit ~ PropD.init, lwd=2, col="#d95f02", xpd=NA, lty=2)
  addpoly(PropD.init, lower, upper, col = alpha("#d95f02", 0.4))
  Mc.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.Med, Species=="Of"), {
  lines(fit ~ PropD.init, lwd=2, col="#1b9e77", xpd=NA, lty=2)
  addpoly(PropD.init, lower, upper, col = alpha("#1b9e77", 0.4))
  Of.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.Med, Species=="Ss"), {
  lines(fit ~ PropD.init, lwd=2, col="#7570b3", xpd=NA, lty=2)
  addpoly(PropD.init, lower, upper, col = alpha("#7570b3", 0.4))
  Ss.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
# Plot lines for High bleaching
with(subset(res.High, Species=="Mc"), {
  lines(fit ~ PropD.init, lwd=2, col="#d95f02", xpd=NA, lty=3)
  addpoly(PropD.init, lower, upper, col = alpha("#d95f02", 0.4))
  Mc.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.High, Species=="Of"), {
  lines(fit ~ PropD.init, lwd=2, col="#1b9e77", xpd=NA, lty=3)
  addpoly(PropD.init, lower, upper, col = alpha("#1b9e77", 0.4))
  Of.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.High, Species=="Ss"), {
  lines(fit ~ PropD.init, lwd=2, col="#7570b3", xpd=NA, lty=3)
  addpoly(PropD.init, lower, upper, col = alpha("#7570b3", 0.4))
  Ss.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
legend("bottomright", bty="n", lty=c(1,2,3), lwd=2, inset=c(0.05, 0),
       legend=c("7 days", "10 days", "14 days"), cex=0.7)
legend("bottomright", bty="n", pch=15, inset=c(0.04, 0.175),
       legend=c("Mcav", "Ssid", "Ofav"), cex=0.7, pt.cex=1.5, x.intersp=1.5,
       col=c("#d95f02", "#7570b3", "#1b9e77"))
#text(par("usr")[1]-par("mai")[2]/2, par("usr")[4], "A.", font=2, xpd=NA)
#text(-0.2, par("usr")[4], "A.", font=2, xpd=NA)
mtext("A.", adj=-0.2, font=2)

# Figure 3B: AUC for each species at each BleachLvl
plot(NA, ylim=c(-1,1), xlim=c(0.5,3.5), xaxs="i", yaxs="i", xaxt="n", 
     xlab="Species", ylab="Symbiont shuffling")
axis(side=1, at=1:3, labels=c("Of", "Ss", "Mc"))
abline(h=0, lty=1, lwd=0.5)
with(auc.list$Low, {
  arrows(0.8:2.8, lower, 0.8:2.8, upper, code=3, length=0.075, angle=90, xpd=NA)
  points(0.8:2.8, fit, pch=15, col=c("#1b9e77", "#7570b3", "#d95f02"), xpd=NA)
})
with(auc.list$Med, {
  arrows(1:3, lower, 1:3, upper, code=3, length=0.075, angle=90, xpd=NA)
  points(1:3, fit, pch=17, col=c("#1b9e77", "#7570b3", "#d95f02"), xpd=NA)
})
with(auc.list$High, {
  arrows(1.2:3.2, lower, 1.2:3.2, upper, code=3, length=0.075, angle=90, xpd=NA)
  points(1.2:3.2, fit, pch=16,  col=c("#1b9e77", "#7570b3", "#d95f02"), xpd=NA)
})
legend("bottomright", bty="n", inset=c(0.05, 0.1),
       pch=c(15, 17, 16), col="black", cex=0.7,
       legend=c("7 days", "10 days", "14 days"))

arrows(par("usr")[2]*0.95, c(0.02, -0.02), 
       par("usr")[2]*0.95, c(0.2, -0.2), length=0.1)
text(par("usr")[2]*0.95, c(0.08, -0.1), pos=2, cex=0.7,
     labels=c("more D1a", "less D1a"))
#text(par("usr")[1]-par("mai")[2]/2, par("usr")[4], "B.", font=2, xpd=NA)
mtext("B.", adj=-0.2, font=2)
dev.off()
```
![Figure 3. Symbiont shuffling in three coral species. Panel **(A)** shows the proportion of clade D *Symbiodinium* before bleaching and after recovery, with the diagonal line of identity representing no change in symbiont proportions. Fitted values for each species (indicated by color) and heat stress duration (indicated by line type) are plotted with shaded areas representing 95% confidence intervals. Panel **(B)** shows the integrated symbiont shuffling response (from before bleaching to after recovery) for each species and bleaching treatment, calculated as the area above or below the diagonal line of identity, normalized to a range of -1 (i.e., a complete loss of clade D symbionts) to +1 (i.e., complete dominance by clade D symbionts).](../figures/Fig3.png)

@@

# Get fitted values and plot shuffling ~ days for different relative advantages of D
stresslevs <- c(0.01, 0.033, 0.05, 0.07, 0.103, 0.163)
cols <- c("gray40", "#1b9e77", "gray40", "gray40", "#7570b3", "#d95f02")
resdf <- expand.grid(days=7:14, ADH=stresslevs)
resdf$fit <- predict(glmod, newdata=resdf, type="response")
resdf$fit.bt <- rescale(resdf$fit, from=c(0,1), to=c(-1,1))
plot(NA, xlim=c(7,14), ylim=c(-1,1), yaxs="r",
     xlab="Days of heat stress",
     ylab="Symbiont shuffling")
mtext("A.", adj=-0.2, font=2)
reslist <- split(resdf, f=resdf$ADH)
for (i in 1:length(reslist)) {
  with(reslist[[i]], lines(fit.bt ~ days, col=cols[i], lwd=2, xpd=NA))
}
abline(h=0, lwd=0.5)
# Get positions for text annotations
angles <- unlist(lapply(reslist, function(x) with(x, fit.bt[2]-fit.bt[1])))
heights <- unlist(lapply(reslist, function(x) with(x, fit.bt[1])))
ADHeat <- expression("A"["Heat"]^"D"~"=")
for (i in 1:length(stresslevs)) {
  text(labels=bquote(.(parse(text=paste(ADHeat,"~",stresslevs[i],sep=""))) ),
       x=7, y=heights[i]-0.06, adj=0, srt=angles[i]*200, cex=0.6)
}
legend("bottomright", bty="n", inset=c(0.05, 0.1),
       lty=1, lwd=2, col=c("#d95f02", "#7570b3", "#1b9e77"), cex=0.7,
       legend=c("Mcav", "Ssid", "Ofav"))

@@

plot(df$shuffle ~ df$ADH.days, ylim=c(-1,1), yaxs="r", xpd=NA,
     pch=c(16,15,17)[as.numeric(as.factor(df$BleachLvl))],
     xlab=expression("A"["Heat"]^"D"~"x (Days of heat stress)"),
     ylab="", mgp=c(1.8,0.1,0),
     col=c("#1b9e77", "#7570b3", "#d95f02")[as.numeric(factor(df$Species))])
mtext("Symbiont shuffling", side=2, line=1.5)
mtext("B.", adj=-0.2, font=2)
lines(seq(0,3,0.1), rescale(predicted, from=c(0,1), to=c(-1,1)), lwd=1)
abline(h=0, lwd=0.5)
text(par("usr")[2]*0.95, c(0.08, -0.1), pos=2, cex=0.7,
     labels=c("more clade D", "less clade D"))
arrows(par("usr")[2]*0.95, c(0.02, -0.02), 
       par("usr")[2]*0.95, c(0.2, -0.2), length=0.1)
legend("bottomright", bty="n", inset=c(0.05, 0.1),
       pch=c(15, 17, 16), col="black", cex=0.7,
       legend=c("7 days", "10 days", "14 days"))
dev.off()
```
![Figure 4. Symbiont shuffling as a function of the photochemical advantage of clade D and heat stress duration. Panel **(A)** shows the symbiont shuffling response (as in Fig. 3B) as a function of heat stress duration (days) and the photochemical advantage of clade D under heat stress (A^D^~Heat~), with lines corresponding to the A^D^~Heat~ values for the three coral species studied (indicated by color), and two hypothetical intermediate values (gray lines). Panel **(B)** shows that the symbiont shuffling responses observed across all three species are predicted well (psuedo-R^2^=0.93) by the time-integrated photochemical advantage of clade D under heat stress.](../figures/Fig4.png)

>>>>

## Plot Figure 1
```{r Fig1}
png("figures/Fig1.png", width=4, height=2.5, units="in", res=300)
par(mfrow=c(1, 3), mar=c(3,3,1.1,0), mgp=c(1.5, 0.1, 0), 
    tcl=0.2, cex.axis=0.8, xaxs="i")
plot(NA, xlim=c(0, 1), ylim=c(0.2, 0.55),
     xlab="Proportion D1a", ylab=expression(italic(F[v]/F[m])))
mtext("a", adj=-0.2, font=2)
with(subset(pred, Species=="Of" & time=="init"), {
  lines(fit ~ PropD, lty=1, lwd=1)
  addpoly(PropD, lci, uci, col=alpha("#1b9e77", 0.5))
})
with(subset(pred, Species=="Of" & time=="bleach"), {
  lines(fit ~ PropD, lty=2, lwd=2)
  addpoly(PropD, lci, uci, col=alpha("#1b9e77", 0.5))
})

par(mar=c(3,1.5,1.1,1.5))
plot(NA, xlim=c(0, 1), ylim=c(0.2, 0.55),
     xlab="Proportion D1a", ylab="")
mtext("b", adj=-0.2, font=2)
with(subset(pred, Species=="Ss" & time=="init"), {
  lines(fit ~ PropD, lty=1, lwd=1)
  addpoly(PropD, lci, uci, col=alpha("#7570b3", 0.5))
})
with(subset(pred, Species=="Ss" & time=="bleach"), {
  lines(fit ~ PropD, lty=2, lwd=2)
  addpoly(PropD, lci, uci, col=alpha("#7570b3", 0.5))
})

par(mar=c(3,0,1.1,3))
plot(NA, xlim=c(0, 1), ylim=c(0.2, 0.55),
     xlab="Proportion D1a", ylab="")
mtext("c", adj=-0.2, font=2)
with(subset(pred, Species=="Mc" & time=="init"), {
  lines(fit ~ PropD, lty=1, lwd=1)
  addpoly(PropD, lci, uci, col=alpha("#d95f02", 0.5))
})
with(subset(pred, Species=="Mc" & time=="bleach"), {
  lines(fit ~ PropD, lty=2, lwd=2)
  addpoly(PropD, lci, uci, col=alpha("#d95f02", 0.5))
})
dev.off()
```
![Figure 1. Photochemical efficiency as a function of the proportion of clade D *Symbiodinium*. Solid lines represent ambient conditions, and dotted lines represent the relationship under heat stress (32°C). Shaded regions represent 90% confidence intervals around fitted values.](../figures/Fig1.png)

@@

```{r Fig3}
# Figure 3
png("figures/Fig3.png", width=7, height=3.5, units="in", res=300)
par(mfrow=c(1, 2), mar=c(3,3,1,1), mgp=c(1.5, 0.1, 0), tcl=0.2, cex.axis=0.8)
## Figure 3A: Final vs. initial proportion clade D
plot(NA, xlim=c(0,1), ylim=c(0,1), xaxs="i", yaxs="i",
     xlab="Prop. D1a before bleaching",
     ylab="Prop. D1a after recovery")
# Plot lines for low bleaching
with(subset(res.Low, Species=="Mc"), {
  lines(fit ~ PropD.init, lwd=2, col="#d95f02", xpd=NA)
  addpoly(PropD.init, lower, upper, col = alpha("#d95f02", 0.4))
  Mc.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.Low, Species=="Of"), {
  lines(fit ~ PropD.init, lwd=2, col="#1b9e77", xpd=NA)
  addpoly(PropD.init, lower, upper, col = alpha("#1b9e77", 0.4))
  Of.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.Low, Species=="Ss"), {
  lines(fit ~ PropD.init, lwd=2, col="#7570b3", xpd=NA)
  addpoly(PropD.init, lower, upper, col = alpha("#7570b3", 0.4))
  Ss.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
abline(0,1, lty=1, lwd=0.5)
# Plot lines for Med bleaching
with(subset(res.Med, Species=="Mc"), {
  lines(fit ~ PropD.init, lwd=2, col="#d95f02", xpd=NA, lty=2)
  addpoly(PropD.init, lower, upper, col = alpha("#d95f02", 0.4))
  Mc.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.Med, Species=="Of"), {
  lines(fit ~ PropD.init, lwd=2, col="#1b9e77", xpd=NA, lty=2)
  addpoly(PropD.init, lower, upper, col = alpha("#1b9e77", 0.4))
  Of.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.Med, Species=="Ss"), {
  lines(fit ~ PropD.init, lwd=2, col="#7570b3", xpd=NA, lty=2)
  addpoly(PropD.init, lower, upper, col = alpha("#7570b3", 0.4))
  Ss.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
# Plot lines for High bleaching
with(subset(res.High, Species=="Mc"), {
  lines(fit ~ PropD.init, lwd=2, col="#d95f02", xpd=NA, lty=3)
  addpoly(PropD.init, lower, upper, col = alpha("#d95f02", 0.4))
  Mc.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.High, Species=="Of"), {
  lines(fit ~ PropD.init, lwd=2, col="#1b9e77", xpd=NA, lty=3)
  addpoly(PropD.init, lower, upper, col = alpha("#1b9e77", 0.4))
  Of.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
with(subset(res.High, Species=="Ss"), {
  lines(fit ~ PropD.init, lwd=2, col="#7570b3", xpd=NA, lty=3)
  addpoly(PropD.init, lower, upper, col = alpha("#7570b3", 0.4))
  Ss.auc <<- c((mean(fit)-0.5)/0.5, (mean(lower)-0.5)/0.5, (mean(upper)-0.5)/0.5)
})
legend("bottomright", bty="n", lty=c(1,2,3), lwd=2, inset=c(0.05, 0),
       legend=c("7 days", "10 days", "14 days"), cex=0.7)
legend("bottomright", bty="n", pch=15, inset=c(0.04, 0.175),
       legend=c("Mcav", "Ssid", "Ofav"), cex=0.7, pt.cex=1.5, x.intersp=1.5,
       col=c("#d95f02", "#7570b3", "#1b9e77"))
#text(par("usr")[1]-par("mai")[2]/2, par("usr")[4], "A.", font=2, xpd=NA)
#text(-0.2, par("usr")[4], "A.", font=2, xpd=NA)
mtext("a", adj=-0.2, font=2)

# Figure 3B: AUC for each species at each BleachLvl
plot(NA, ylim=c(-1,1), xlim=c(0.5,3.5), xaxs="i", yaxs="i", xaxt="n", 
     xlab="Species", ylab="Symbiont shuffling")
axis(side=1, at=1:3, labels=c("Ofav", "Ssid", "Mcav"))
abline(h=0, lty=1, lwd=0.5)
with(auc.list$Low, {
  arrows(0.8:2.8, lower, 0.8:2.8, upper, code=3, length=0.075, angle=90, xpd=NA)
  points(0.8:2.8, fit, pch=15, col=c("#1b9e77", "#7570b3", "#d95f02"), xpd=NA)
})
with(auc.list$Med, {
  arrows(1:3, lower, 1:3, upper, code=3, length=0.075, angle=90, xpd=NA)
  points(1:3, fit, pch=17, col=c("#1b9e77", "#7570b3", "#d95f02"), xpd=NA)
})
with(auc.list$High, {
  arrows(1.2:3.2, lower, 1.2:3.2, upper, code=3, length=0.075, angle=90, xpd=NA)
  points(1.2:3.2, fit, pch=16,  col=c("#1b9e77", "#7570b3", "#d95f02"), xpd=NA)
})
legend("bottomright", bty="n", inset=c(0.05, 0.1),
       pch=c(15, 17, 16), col="black", cex=0.7,
       legend=c("7 days", "10 days", "14 days"))

arrows(par("usr")[2]*0.95, c(0.02, -0.02), 
       par("usr")[2]*0.95, c(0.2, -0.2), length=0.1)
text(par("usr")[2]*0.95, c(0.08, -0.1), pos=2, cex=0.7,
     labels=c("more D1a", "less D1a"))
#text(par("usr")[1]-par("mai")[2]/2, par("usr")[4], "B.", font=2, xpd=NA)
mtext("b", adj=-0.2, font=2)
dev.off()
```
![Figure 3. Symbiont shuffling in three coral species. Panel **(A)** shows the proportion of clade D *Symbiodinium* before bleaching and after recovery, with the diagonal line of identity representing no change in symbiont proportions. Fitted values for each species (indicated by color) and heat stress duration (indicated by line type) are plotted with shaded areas representing 95% confidence intervals. Panel **(B)** shows the integrated symbiont shuffling response (from before bleaching to after recovery) for each species and bleaching treatment, calculated as the area above or below the diagonal line of identity, normalized to a range of -1 (i.e., a complete loss of clade D symbionts) to +1 (i.e., complete dominance by clade D symbionts).](../figures/Fig3.png)

@@

# Get fitted values and plot shuffling ~ days for different relative advantages of D
stresslevs <- c(0.01, 0.033, 0.05, 0.07, 0.103, 0.163)
cols <- c("gray40", "#1b9e77", "gray40", "gray40", "#7570b3", "#d95f02")
resdf <- expand.grid(days=7:14, ADH=stresslevs)
resdf$fit <- predict(glmod, newdata=resdf, type="response")
resdf$fit.bt <- rescale(resdf$fit, from=c(0,1), to=c(-1,1))
plot(NA, xlim=c(7,14), ylim=c(-1,1), yaxs="r",
     xlab="Days of heat stress",
     ylab="Symbiont shuffling")
mtext("a", adj=-0.2, font=2)
reslist <- split(resdf, f=resdf$ADH)
for (i in 1:length(reslist)) {
  with(reslist[[i]], lines(fit.bt ~ days, col=cols[i], lwd=2, xpd=NA))
}
abline(h=0, lwd=0.5)
# Get positions for text annotations
angles <- unlist(lapply(reslist, function(x) with(x, fit.bt[2]-fit.bt[1])))
heights <- unlist(lapply(reslist, function(x) with(x, fit.bt[1])))
ADHeat <- expression("A"["Heat"]^"D"~"=")
for (i in 1:length(stresslevs)) {
  text(labels=bquote(.(parse(text=paste(ADHeat,"~",stresslevs[i],sep=""))) ),
       x=7, y=heights[i]-0.06, adj=0, srt=angles[i]*200, cex=0.6)
}
legend("bottomright", bty="n", inset=c(0.05, 0.1),
       lty=1, lwd=2, col=c("#d95f02", "#7570b3", "#1b9e77"), cex=0.7,
       legend=c("Mcav", "Ssid", "Ofav"))

@@

plot(df$shuffle ~ df$ADH.days, ylim=c(-1,1), yaxs="r", xpd=NA,
     pch=c(16,15,17)[as.numeric(as.factor(df$BleachLvl))],
     xlab=expression("A"["Heat"]^"D"~"x (Days of heat stress)"),
     ylab="", mgp=c(1.8,0.1,0),
     col=c("#1b9e77", "#7570b3", "#d95f02")[as.numeric(factor(df$Species))])
mtext("Symbiont shuffling", side=2, line=1.5)
mtext("b", adj=-0.2, font=2)
lines(seq(0,3,0.1), rescale(predicted, from=c(0,1), to=c(-1,1)), lwd=1)
abline(h=0, lwd=0.5)
text(par("usr")[2]*0.95, c(0.08, -0.1), pos=2, cex=0.7,
     labels=c("more clade D", "less clade D"))
arrows(par("usr")[2]*0.95, c(0.02, -0.02), 
       par("usr")[2]*0.95, c(0.2, -0.2), length=0.1)
legend("bottomright", bty="n", inset=c(0.05, 0.1),
       pch=c(15, 17, 16), col="black", cex=0.7,
       legend=c("7 days", "10 days", "14 days"))
dev.off()
```
![Figure 4. Symbiont shuffling as a function of the photochemical advantage of clade D and heat stress duration. Panel **(A)** shows the symbiont shuffling response (as in Fig. 3B) as a function of heat stress duration (days) and the photochemical advantage of clade D under heat stress (A^D^~Heat~), with lines corresponding to the A^D^~Heat~ values for the three coral species studied (indicated by color), and two hypothetical intermediate values (gray lines). Panel **(B)** shows that the symbiont shuffling responses observed across all three species are predicted well (psuedo-R^2^=0.93) by the time-integrated photochemical advantage of clade D under heat stress.](../figures/Fig4.png)
